---
title: "The title"
author: "Your Name"
subtitle: Some subtitle
output:
  ioslides_presentation: default
  beamer_presentation:
    slide_level: 1
    theme: AnnArbor
    keep_tex: no
  slidy_presentation: default
institute: Your Affiliation
header-includes:
- \input{subfiles/smipstyle.tex}
- \titlegraphic{\includegraphics[width=4cm]{subfiles/mannheim}}
- \AtBeginDocument{\date[Conference/Occasion]{Conference/Occasion, April 2, 4242}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, collapse = TRUE)
# load packages and define functions here
```


# Slide Title

This is how you itemize:

- Main point
  - Sub-point (level 1) 
    - Sub-point (level 2)


This is regular text.

\emph{This is how you emphasize}.

\highlight{This text is highlighted.}

\deemph{This line is not important (de-emphasized).}



# How to Display Code

This code chunk will be printed...

```{r echo=TRUE}
1 + 1
```

... this one won't:

```{r}
1 + 1
```




# Don't forget to thank the DFG :-)

\vspace{1cm}

\begin{columns} 
\begin{column}{.48\textwidth} 

\begin{figure}[p]
```{r, out.width = "150px", fig.align = 'center'}
knitr::include_graphics('subfiles/logo_full.eps')
```
\end{figure}

\end{column}
\begin{column}{.48\textwidth} 

\begin{center}

\footnotesize{This research was funded by the Deutsche Forschungsgemeinschaft (DFG), grant 2277, Research Training Group ``Statistical Modeling in Psychology" (SMiP)}

\end{center}

\end{column}
\end{columns}

\vspace{1cm}

This is how you can specify columns, by the way. 



