---
title: "CAMtools"
subtitle: "An introductory workshop"
author: "Julius Fenn"
date: "2023-11-23"
# institute: Your Affiliation

format:
  revealjs:
    theme: white # gerne herumspielen!
    #theme: [white, custom.scss] # gerne herumspielen!
---

```{r}
knitr::opts_chunk$set(echo = FALSE, collapse = TRUE)

# load packages and define functions here

################
# Packages
################
# if packages are not already installed, the function will install and activate them
usePackage <- function(p) {
  if (!is.element(p, installed.packages()[,1]))
    install.packages(p, dep = TRUE)
  require(p, character.only = TRUE)
}

usePackage("stargazer") # create tables

usePackage("tidyverse")

usePackage("DT")

usePackage("RefManageR")

usePackage("meta")

usePackage("lsa")

usePackage("mvtnorm")

################
# Data Bib file
################
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           style = "markdown",
           dashed = TRUE,
           longnamesfirst = FALSE,
           max.names = 1,
           no.print.fields = c("urldate", "note"))
file.name <- "JuliusLibrary.bib"
bib <- ReadBib(file.name)
```


# Part I: Overview

## CAMS Overview
This is how you itemize:

- Main point
  - Sub-point (level 1) 
    - Sub-point (level 2)


This is regular text with a citation
`r Citet(bib, "aggarwalNeuralNetworksDeep2023")`


## Motivating Graph Theory (Network Analysis)


## Related literature

This code chunk will be printed...

```{r}
#| echo: true
1 + 1
```

... this one won't:

```{r}
#| echo: false
1 + 1
```


# Part II: CAMs

## Recap: Existing Literature



## Coherence Theory and the HOTCO Model


## CAM Study Designs and Resulting Network Topologies



# Part III: Developed CAM Tools


## Data Collection: C.A.M.E.L



## Data Analysis: CAM-App


## Setting Up Studies



# Don't forget to thank the DFG :-)

This research was funded by the Deutsche Forschungsgemeinschaft (DFG), grant 2277, Research Training Group ``Statistical Modeling in Psychology" (SMiP)


# References

<!-- *********** NEW SLIDE ************** -->
---
## References I

```{r}
#| echo: false
#| results: asis
PrintBibliography(bib, start = 1, end = 5)
```
