---
title: "CAMtools"
subtitle: "An introductory workshop"
author: "Julius Fenn"
date: "2023-11-23"
# institute: Your Affiliation

format:
  revealjs:
    theme: white # gerne herumspielen!
    #theme: [white, custom.scss] # gerne herumspielen!
---

```{r}
knitr::opts_chunk$set(echo = FALSE, collapse = TRUE)
# load packages and define functions here
```


# Part I: Overview

## CAMS Overview
This is how you itemize:

- Main point
  - Sub-point (level 1) 
    - Sub-point (level 2)


This is regular text.

## Motivating Graph Theory (Network Analysis)


## Related literature

This code chunk will be printed...

```{r}
#| echo: true
1 + 1
```

... this one won't:

```{r}
#| echo: false
1 + 1
```


# Part II: CAMs

## Recap: Existing Literature



## Coherence Theory and the HOTCO Model


## CAM Study Designs and Resulting Network Topologies



# Part III: Developed CAM Tools


## Data Collection: C.A.M.E.L



## Data Analysis: CAM-App


## Setting Up Studies



# Don't forget to thank the DFG :-)

This research was funded by the Deutsche Forschungsgemeinschaft (DFG), grant 2277, Research Training Group ``Statistical Modeling in Psychology" (SMiP)